% Modification of moderncv's "template.tex" example.
%
% Type: Generic
% Description: This is the generic, untailored version of my CV
\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{ifthen}

% CONSTANTS
\newcommand{\usestylemodern}{Modern}
\newcommand{\usestyletraditional}{Traditional}

% CONFIG
\newcommand{\bccvstyle}{Modern} % Modern or Traditional style.

% build.ps1 can override the style
\ifdefined\bccvstyleoverride
    \renewcommand{\bccvstyle}{\bccvstyleoverride}
\fi

% Select theme based off of \bccvstyle config
\ifthenelse{\equal{\bccvstyle}{\usestylemodern}}
{
    \moderncvstyle{casual}
    \moderncvcolor{blue}
    \let\usestyletraditional\undefined
}
{
    \moderncvstyle{banking}
    \moderncvcolor{black}
    \let\usestylemodern\undefined
}

% Use serif by default
\renewcommand{\familydefault}{\sfdefault}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}

% personal data
\name{Bradley}{Chatha}
\title{}
\address{Warwickshire, Nuneaton-Coventry-Birmingham Area}{}
\phone[mobile]{+44~7506701660}
\email{bradley@chatha.dev}
\homepage{bradley.chatha.dev}
\social[linkedin]{bradley-chatha}
\social[twitter]{@BradleyChatha}
\social[github]{BradleyChatha}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Qualifications}
\cventry{2017--2020}{Various subjects}{AIM Educational Ltd}{Atherstone}{}
{
    \begin{itemize}
        \item Level 2 Mathematics
        \item Level 2 English Reading \& Writing
        \item Level 2 Catering
        \item Level 2 Employability
    \end{itemize}
}
\cventry{2015--2017}{Level 3 Computer Science (A Level)}{Pembrokeshire College}{}{B}
{
}

\section{Experience}
\cventry{2017--2020}{Work Experience - Student Developer Aide}{AIM Educational Ltd}{Atherstone}{}
{
    Alongside my status as a student, my capabilities allowed me to work on
    several projects for AIM:
    \begin{itemize}
        \item FarmMaster (C\#, ASP Core, PSQL, SASS, Gulp, Webpack, JS\&TS, EF Core, Vue, GraphQL)
        \begin{itemize}
            \item A WIP Website solution used to keep track of and manage livestock.
            \item I was the sole, full-stack developer of this project.
        \end{itemize}
        \item AimCLITool (D, Docker)
        \begin{itemize}
            \item A custom CLI tool used to easily manage various needs I have, such as automatic deployment and secrets management.
            \item Built on top of my custom CLI and Dependency Injection frameworks: JCLI (D), and JIOC (D)
        \end{itemize}
        \item PolyMaster (Likely: Same as FarmMaster, but with Arduino/ESP32 added)
        \begin{itemize}
            \item The project was in the pre-planning stage, it would've been used to automatically manage AIM's new polytunnel.
            \item Arduinos/ESP32s would have been used to monitor and automate various parts of the polytunnel.
            \item A web interface would have been provided to monitor/interact with the various aspects that PolyMaster could manage.
        \end{itemize}
    \end{itemize}
}

\section{Skills}
\cvitem{Misc}{Good time-keeping; Hard worker; Self-motivating; Ability to self-teach.}
\cvitem{Misc}{Works well independently; Quick learner.}

\section{Hobbies}
\cvitem{Coding}{I maintain two open source D libraries - JCLI, and JANSI. I also have a few side projects.}
\cvitem{Gaming}{I'm a fan of a wide variety of genres.}

\section{Awards}
\cventry{28th June 2019}{School Farm Innovation Award}{School Farm Network}{Royal Agricultural University}{}{}

\section{References}
\cvitem{Andy Radford}{Owner of AIM Educational Ltd - Previous owner and developer of a PoS software company.}
\cvitem{Deborah Wagg}{Headteacher and Mathematics teacher of AIM Educational Ltd.}

% START Modern CV page
% Traditional CVs are only one page, Modern can be two (sometimes three!)
\ifdefined\usestylemodern
\newpage

\section{Blogging}
\cvitem{}
{
    On my personal website (see footer) I host my blog, which currently contains:
    \begin{itemize}
        \item A short tutorial series covering the vast metaprogramming power of D, by creating a JSON serialiser.
        \item A tutorial series showing misc. projects where D can let you do complex things easily using metaprogramming.
        \item A changelog for my CLI library - JCLI.
    \end{itemize}
}

\section{Contributions \& Projects}
\cvitem{DLang}
{
    I have made several contributions to the D programming language and its community, such as:
    Documentation and additions for Phobos - the standard library, fixes \& additions to public D libraries, and the creation of my blog
    which as stated previously, features D.
}
\cvitem{JCLI}
{
    I currently maintain an open-source library called 'JCLI'. A D library used to help create
    command line interface tooling.
}
\cvitem{JANSI}
{
    I also maintain an ANSI (SGR) library in D which aids in the ability to output and also parse ANSI-encoded text.
}
\cvitem{SdlangSharp}
{
    A C\# library that is accelerated by SIMD intrinsics to quickly parse .sdl files into tokens or a DOM.
}

\section{Learning Resources}
\cvitem{Obvious}{Google; Stackoverflow; MDN; docs.microsoft.com; Youtube}
\cvitem{Book}{Clean Architecture by Robert C. Martin}
\cvitem{Book}{Clean Code by Robert C. Martin}
\cvitem{Book}{Programming in D by Ali Çehreli}
\cvitem{Book}{Game Programming Patterns by Robert Nystrom}
\cvitem{Webinar}{Microsoft Azure Virtual Training Day: Fundamentals}
\cvitem{Website}{vulkan-tutorial.com - For Vulkan, a very low-level GPU API.}

\fi
% END Modern CV page

\end{document}